\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage[a4paper,margin=0.75in]{geometry}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4}
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\setlength{\footskip}{4.1pt}

\begin{document}

\begin{center}
  \textbf{\Huge \scshape Ankit Kumar Sahu} \\
  \small Ranchi, India $|$ \href{mailto:sahuankit.murhu@gmail.com}{\underline{sahuankit.murhu@gmail.com}} $|$
  \href{https://www.linkedin.com/in/kmrankitt/}{\underline{linkedin.com/}}
  \href{https://github.com/kmr-ankitt}{\underline{github.com/}}
  \href{https://leetcode.com/u/kmrankit/}{\underline{leetcode.com/}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
B.Tech student in Computer Science and Engineering with a focus on full-stack development, cross-platform applications,  Data structures and low-level systems. Passionate about open-source contributions and building efficient software solutions.   

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\resumeItemListStart

\resumeItem{\textbf{Languages:} TypeScript, C++, Go, Rust, Python, C, Java, Bash}
\resumeItem{\textbf{Frameworks \& Libraries:} React, Next.js, Express.js, Gin, React Native, FastAPI, Flask}
\resumeItem{\textbf{Databases \& ORMs:} PostgreSQL, MongoDB, Redis, SQLite, Prisma, Drizzle}
\resumeItem{\textbf{Tools \& Technologies:} Linux, Compilers, Docker, Git, Apache Kafka, AWS, CI/CD, CMake, Ninja}

\resumeItemListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading{\textbf{Devide} $|$ \emph{Multi-lang Web IDE (Next.js)}}{\href{https://github.com/kmr-ankitt/devide}{GitHub}}
\resumeItemListStart
\resumeItem{Created a web-based IDE supporting multiple programming languages.}
\resumeItem{Implemented a real-time, browser-based coding environment.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Webuild} $|$ \emph{AI-Powered Website Builder (React.js, Express.js, TypeScript)}}{\href{https://github.com/kmr-ankitt/webuild}{GitHub}}
\resumeItemListStart
\resumeItem{Developed an AI-powered platform that generates websites based on user prompts.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Szare} $|$ \emph{Offline File Sharing (Gin, Next.js)}}{\href{https://github.com/kmr-ankitt/szare}{GitHub}}
\resumeItemListStart
\resumeItem{Built a peer-to-peer file-sharing platform with QR-based connectivity.}
\resumeItem{Implemented efficient file transfer with Go and Gin.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Cax} $|$ \emph{Terminal Text Editor (C)}}{\href{https://github.com/kmr-ankitt/cax}{GitHub}}
\resumeItemListStart
\resumeItem{Developed a lightweight terminal-based text editor with essential features.}
\resumeItem{Focused on performance and minimal memory footprint.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{S-lang} $|$ \emph{Programming Language (Typescript)}}{\href{https://github.com/kmr-ankitt/s-lang}{GitHub}}
\resumeItemListStart
\resumeItem{S-lang is a Dynamically typed and Object Oriented Language. }
\resumeItem{Designed for simplicity and ease of use.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Zealot} $|$ \emph{Interpreter and Programming Language (Java)}}{\href{https://github.com/kmr-ankitt/zealot}{GitHub}}
\resumeItemListStart
\resumeItem{Designed an experimental interpreter for a custom programming language.}
\resumeItem{Implemented parsing and execution of user-defined scripts.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION----------- 
\section{Education}
\resumeSubHeadingListStart

\resumeSubheading
{CV Raman Global University, Bhubaneswar}{Bhubaneswar, India}
{Bachelor of Technology in Computer Science and Engineering}{(2023 -- Present) | CGPA: 8.16 }

\resumeSubheading
{Delhi Public School, Ranchi}{Ranchi, India}
{Class 12th, CBSE}{2023 | Percentage: 85\%}

\resumeSubheading
{SS DAV Centenary Public School, Khunti}{Khunti, India}
{Class 10th, CBSE}{2021 | Percentage: 93\%}

\resumeSubHeadingListEnd


\end{document}

